HTW E1 Testing

### 2023-08-21 Analysis/e1_test.qmd
brms posterior predictive checks

>>>>

## Appendix

Posterior Predictive
```{r fig.width=12, fig.height=12}

vx_pred <- 
  posterior_predict(e1_vxBMM, ndraws = 500) |> 
  array_branch(margin=1) |> 
   map_dfr( 
    function(yrep_iter) {
      test  |>
        mutate(vx_pred = yrep_iter)
    },
    .id = 'iter'
  ) |>
  mutate(iter = as.numeric(iter))

vx_pred  |>
  filter(iter < 100) %>%
  ggplot(aes(vx_pred, group = iter)) +
  geom_line(alpha = .05, stat = 'density', color = 'blue') +
  geom_density(data = test,
               aes(vx,col=vb),
               inherit.aes = FALSE,
               size = 0.5) + # 1
  facet_grid(condit ~ vb) +
  xlab('vx')

{
vx_pred  |>
  filter(iter < 100)  |> group_by(id,condit,vb,iter) |>
  summarise(vx_pred=mean(vx_pred)) %>%
  ggplot(aes(x=vb,y=vx_pred, group = vb,fill=vb)) + 
  geom_flat_violin( position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,
                   trim = FALSE,
                   alpha = .5,
                   colour = NA) +
  geom_point(aes(x = as.numeric(vb) - 0.15, y = vx_pred, colour = vb),
             # position = position_jitter(width = 0.05),
             position = position_jitter(width = 0.05, height = 0),
             size = 1,
             shape = 20) +
  geom_boxplot(aes(x = vb, y = vx_pred, fill = vb),
               outlier.shape = NA,
               alpha = 0.5,
               width = 0.1,
               colour = "black") +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + facet_wrap(~condit,ncol=2) + ggtitle("Predicted Vx")  } /
{
vx_pred  |>
  filter(iter < 2)  |> group_by(id,condit,vb) |>
  summarise(vx=mean(vx)) %>%
  ggplot(aes(x=vb,y=vx, group = vb,fill=vb)) + 
  geom_flat_violin( position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,
                   trim = FALSE,
                   alpha = .5,
                   colour = NA) +
  geom_point(aes(x = as.numeric(vb) - 0.15),
             # position = position_jitter(width = 0.05),
             position = position_jitter(width = 0.05, height = 0),
             size = 1,
             shape = 20) +
  geom_boxplot(
               outlier.shape = NA,
               alpha = 0.5,
               width = 0.1,
               colour = "black") +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + facet_wrap(~condit,ncol=2) + ggtitle("Empirical Vx") }
```
